\plaintitle

### 2018-04-05 paper/paper.tex
...

% Copyright
\CopyrightYear{2018}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{UIST'18,}{May 07--12, 2016, San Jose, CA, USA}
%Price
\acmPrice{\$15.00}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Bridging the Translation Gap with ExpandHelp}
\def\plainauthor{First Author, Second Author, Third Author,
  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{Authors' choice; of terms; separated; by
  semicolons; include commas, within terms only; required.}
\def\plaingeneralterms{Documentation, Standardization}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\def\GIT{\texttt{git}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\numberofauthors{3}
\author{%
  \alignauthor{Toshiyuki Masui
    \affaddr{Keio University}\\
    \affaddr{Fujisawa, Japan}\\
    \email{masui@pitecan.com}}\\
  \alignauthor{Jun Kato\\
    \affaddr{AIST}\\
    \affaddr{Tsukuba, Japan}\\
    \email{junkato}}\\
}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  %
  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
  % he may have to translate his intention into an English expression ``make the room darker'',
  he may have to find that he should ``turn off the ceiling light'' for the task,
  translate it to a required action ``toggle the wall switch''
  or a command like ``\tt{\$ iot clight 0}''.
  %
  % When a user wants to ``make the room darker'',
  % he should translate it to a real action like ``turn off the ceiling light''.
  % To do so,
  % he may have to ``toggle the wall switch''
  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  % If the user is a Chinese speaker, he might have to translate his intention
  % ``房間暗一点'' into ``make the room darker'',
  % ``turn off the ceiling light'', 
  % ``toggle the wall switch'',
  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
  %
  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex {\GIT} commands
  from fragments of users' intentions.
\end{abstract}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

@@

When people want to perform a task using modern artifacts,
people frequently find difficulty handling them properly.
%
Even when manuals and help systems are provided,
people don't use them\cite{Novick:2006:WDP:1166324.1166329}
partly because of the vocabulary problem\cite{Furnas:1987:VPH:32206.32212}.
%
% Twitterでのアンケート: 80\% が全然使わない
% https://gyazo.com/2dd525388cce34c916638f51bad386c7
% 
% やりたいと思ったことがすぐできればどれほど嬉しいことか
% そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
%
We should translate our vague intentions in our brain into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
All the living creatures are performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.

Even when people vaguely know what they have to do for what they want to do,
it is often not easy for them to perform the task properly.
Even when people know that they can watch a movie on the Internet,
finding a movie and playing it is a difficult task for people without experiences.
It would be nicer if they could watch a movie on the net
just by showing a vague title or attributes of the movie
in various languages.

@@

We propose a simple, flexible and powerful
translation framework with which users can generate a complete
command string from fragments of users' vague intentions.
%
We provide a database consisting of pairs of
the description of the task that users want to perform (e.g. 房間暗一点)
and
the actual command string required by the system (e.g. \tt{\$ iot clight 0}).
Descriptions can be written in any natural language using regular expressions
and the database on the Wiki pages can be edited by any user
who wants to improve the database.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct instruction to an artifact from
  the user's vague intention in natural language.
\item General-purpose flexible dynamic search system based on regular expressions.
% そのための柔軟なインフラ (ExpandHelp)
% \item IME-like command etnry interface
% やりたいことを実行するインタフェース (IME的なもの)
\item Data sharing infrastructure for the above strategy.
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

\subsection{Entering a command}

We assume that the user uses \tt{bash} for his software
development activities.

% \begin{figure}[h]
%   \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
%   \caption{Bash shell.}
%   \label{bash1}
% \end{figure}

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use {\GIT} with an argument
``\verb|HEAD^^|''
for specifying the old version.

\begin{quotation}
  \verb|$ git diff HEAD^^ README.md|
  \par
  \verb|$|
\end{quotation}

However, nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command above only compares the \stt{README.md}
with the file included in an old commit, where
\stt{README.md} might be the same as the latest version.

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing \stt{git RE 2} to see how he can
perform the task.

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH} after typing \stt{git rea 2}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}''.
If the user thinks that that's what he wants to do,
he can select the entry by typing arrow keys and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like \sqsf{2 days ago} is also shown in the candidate list.
This means that the user can use the same string \sqtt{git RE 2}
for getting the \stt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
may not be familiar to most {\GIT} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.

A Japanese {\GIT} user can do the same thing just like
English-speaking users.
He can user the term \qtt{比}(compare) to find how he can perfor the job.

\begin{figure}[t]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
button and see the Wiki page shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.

\begin{figure}[b]
\begin{verbatim}
\end{verbatim}
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
\caption{A {\SB} page for \tt{git diff}.}
\label{scrapboxpage}
\end{figure}

@@

A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.
%
Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents the help entry description
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be like this:

\begin{quote}
  \textbf{description}: \\
  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
  \textbf{command}: \\
  {\fontsize{9pt}{0pt}\selectfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\sqsf{Compare README.md with the one from 1 versions before}, 
\sqsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a {\GIT} command.
In the first example, \sqsf{README.md} and \sqsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.

@@

% When the matched pattern like \qsf{San Francisco}
% cannot be directly used in the command,
% parameters for the command can be put after the description string,
% separated by a TAB character.
% For example, when a number like ``\tt{29247}'' should be used
% for checking the
% weather of San Francisco, we can describe the help entry like this:
% 
% \begin{quote}\small
%  description: \\
%  \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
%  command: \\
%  \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
% \end{quote}
%
% Here, selecting a menu entry \qsf{Check the weather of San Francisco}
% will produce a command
% \tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.

@@

Finding appropriate entries from the huge help document space is performed in two steps.
First, a state transition diagram is generated from the regular expressions
used in the descriptions.
Second, all the description strings are generated by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions in a short form.
For example, we use a short regular expression
\sqtt{(remove|delete|erase) (data|file)}
for representing expressions like
\sqsf{remove data},\sqsf{erase file}, etc.

Converting a regular expression to a state transition machine is a straightforward task.
When we have a regular expression
\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
we can parse the string and convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
\caption{State transition diagram for finding a restaurant.}
\label{statemachine1}
\end{figure}

@@

\begin{quote}
\small
\ssf{Compare README.md with the one 1 versions before} \\
\ssf{Compare index.html with the one 1 versions before} \\
...\\
\ssf{Compare package.json with the one 10 versions beforef}\\
\end{quote}

@@

``Generate-and-test''\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}
is a simple and effective strategy
used for solving puzzles and AI problems.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

\begin{figure}[h]
  \includegraphics[width=60mm,bb=0 0 439 73]{figures/readme1.pdf}
  \caption{A state machine for \qsf{README}.}
  \label{readme1}
\end{figure}

Initially, only the leftmost node is active, but when the
state machine receives \qsf{R}, both the first and the second node become active
and the activation state will change to the following pattern.

\begin{figure}[h]
\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme2.pdf}
\caption{After receiving \qsf{R}.}
\label{readme2}
\end{figure}

When \qsf{README} is given to the state machine,
the rightmost node becomes active.

\begin{figure}[h]
\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
\caption{After receiving \qsf{README}.}
\label{readme3}
\end{figure}

Although this state machine is a nondeterministic finite automata (NFA),
only 10 bits are required to represent the active/inactive states of the nodes,
meaning that the whole states can be represented by a single integer value.
Also,
the state transition can be calculated by a simple combination of
logic and bit shift operations.

%% We will describe how the pattern matching can be performed using a C code.
%% 
%% First, a variable for current state is
%% set to \stt{0x80000000}, representing the initial pattern
%% shown in Figure \ref{readme1}.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  #define INITPAT 0x80000000
%%  int state = INITPAT;
%% \end{verbatim}
%% }
%% 
%% When character \qsf{r} is received, the MSB will be shifted to the right
%% by one bit, and logical OR is calculated with the initial value, \stt{0x80000000}.
%% Since the 7th node also accepts \qsf{r}, it should also be shifted.
%% The state transition can be described like below.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  mask['r'] = 0x82;
%%  state = INITPAT | ((state & mask['r']) >> 1);
%% \end{verbatim}
%% }
%% 
%% The shift ``mask'' value can be easily calculated from the given
%% pattern string beforehand.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%   int maskpat;
%%   init(pat){
%%     maskpat= INITPAT;
%%     for(char *s=pat;*s;s++){
%%       mask[*s] |= maskpat;
%%       maskpat >>= 1;
%%     }
%%     acceptpat = maskpat;
%%   }
%% \end{verbatim}
%% }
%% 
%% The pattern matching function can be described like below.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  match(s){
%%    int state = INITPAT;
%%    for(s=text;*s;s++){
%%      state = INITPAT | ((state & mask[*s]) >> 1);
%%    }
%%    return ((state & acceptpat) != 0);
%%  }
%% \end{verbatim}
%% }

\subsubsection{Approximate pattern matching using the shifter algorithm}

The state machine shown in Figure \ref{readme1} can accept only one pattern
(\sqsf{README}), but
it can be easily expanded to detect texts which contain a word
similar to the pattern (e.g. \sqsf{READY}).

%   *  ** 
%  risto rante
%  restaurant
\begin{figure}[htb]
  \centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
  \caption{Matching error between \qsf{README} and \qsf{REDDY}.}
  \label{readme-reddy-mismatch}
\end{figure}

Adding three more states to Figure \ref{readme1}, we can perform more
flexible pattern matcher which can accept strings with
0 to 3 matching errors.

\begin{figure}[htb]
  \includegraphics[width=65mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
  \caption{A pattern matcher accepting 0-3 errors.}
  \label{shifterambig}
\end{figure}

Figure \ref{shifterambig} shows a state machine which can detect a string
which matches \sqsf{README} with 0 to 3 mismatches.
Each additional row of nodes represents a matcher with one error,
two errors, and three errors, respectively.
Vertical and diagonal transition edges are added to allow
transitions based on spelling errors.

@@

% \begin{figure}[htb]
% \includegraphics[width=82mm]{figures/restaurant-ristrante.pdf}
% \caption{Accepting ``\tsf{ristorante}'' using a matcher for ``\tsf{restaurant}''.}
% \label{restaurant-ristorante}
% \end{figure}

The transition of active nodes while reading
\sqsf{REDDY} is shown in Figure \ref{restaurant-ristorante}.
After reading \sqsf{REDDY},
only the upper-right node becomes active,
denoting that \sqsf{REDDY} matches
\sqsf{README}'' with 3 matching errors.

The state transition shown in 
Figure \ref{restaurant-ristorante} looks complicated, but
the matching state can be represented by only four integer variables, and
the matching algorithm is not very different from the algorithm
shown above.

@@

Since the translation mechanism of {\EH} is simple and flexible,
it can be used for a wide range of application domains where
intelligent help is required.
{\EH} can be used for

>>>>

% Copyright
\CopyrightYear{2018}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{UIST'18,}{October 14--17, 2018, Berlin, Germany}
%Price
\acmPrice{\$15.00}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Bridging the Translation Gap with ExpandHelp}
\def\plainauthor{Toshiyuki Masui, Jun Kato}
\def\emptyauthor{}
\def\plainkeywords{
  Help systems; Regular expression, Input method, Generate and filter;
  ExpandHelp; GitHelp
}
% \def\plaingeneralterms{Documentation, Standardization}

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\def\GIT{\texttt{git}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}
\long\def\smallfont{\fontsize{9pt}{0pt}\selectfont}

@@

\numberofauthors{3}
\author{%
  \alignauthor{Toshiyuki Masui \\
    \affaddr{Keio University}\\
    \affaddr{Fujisawa, Japan}\\
    \email{masui@pitecan.com}}\\
  \alignauthor{Jun Kato\\
    \affaddr{AIST}\\
    \affaddr{Tsukuba, Japan}\\
    \email{junkato}}\\
}

@@

\begin{abstract}
  We introduce a flexible command translation framework that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and required actions.
  % the language and vocabularies used for the task are completely different.
  %
  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
  % he may have to translate his intention into an English expression ``make the room darker'',
  he may have to find that he should ``turn off the ceiling light'' for the task,
  translate it to a required action ``toggle the wall switch''
  or a command like ``\tt{\$ iot clight 0}''.
  %
  % When a user wants to ``make the room darker'',
  % he should translate it to a real action like ``turn off the ceiling light''.
  % To do so,
  % he may have to ``toggle the wall switch''
  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  % If the user is a Chinese speaker, he might have to translate his intention
  % ``房間暗一点'' into ``make the room darker'',
  % ``turn off the ceiling light'', 
  % ``toggle the wall switch'',
  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
  %
  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people
  whose mother languages are far from the command syntax required for
  handling computers.
  %
  We propose a simple and flexible translation framework
  {\EH} that can be used in various situations
  where such translation is necessary.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex {\GIT} commands
  from fragments of users' intentions in various languages.
\end{abstract}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous}

% \category{See
%   \url{http://acm.org/about/class/1998/} for the full list of ACM
%   classifiers. This section is required.}{}{}

@@

When people want to perform a task using modern artifacts,
people frequently find difficulty handling them properly.
%
Even when manuals and help documents are provided,
people don't use them\cite{Novick:2006:WDP:1166324.1166329}
partly because of the vocabulary problem\cite{Furnas:1987:VPH:32206.32212}.
%
% Twitterでのアンケート: 80\% が全然使わない
% https://gyazo.com/2dd525388cce34c916638f51bad386c7
% 
% やりたいと思ったことがすぐできればどれほど嬉しいことか
% そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
%
We should translate our vague intentions in our brain into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
In either of these cases, there is a tremendous gap
betwee the user's intentions and required actions.
All the living creatures are seemingly performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.

Even when people almost know what they have to do,
it is often not easy for them to perform the task without confusion.
Even when people know that they can watch a movie on the Internet,
finding a movie and playing it is a difficult task for people without experiences.
It would be nicer if they could watch a movie
just by showing a fragment of the title or attributes of the movie.

@@

We propose a simple, flexible and powerful
translation framework {\EH}, with which users can generate a complete
command string from fragments of users' vague intentions.
%
We use a database consisting of pairs of
the description of the task that users want to perform (e.g. 房間暗一点)
and
the actual command string required by the system (e.g. \tt{\$ iot clight 0}).
Descriptions can be written in any natural language using regular expressions
and the database are shared on the Wiki pages and can be edited by any user
who wants to improve the database.

@@

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of ``\textit{translation paradigm}'' for
  generating a correct command to an artifact from
  the user's vague intention.
\item Flexible dynamic help extraction algorithm
  ``\textit{generate and filter}''
  using regular expressions.
% そのための柔軟なインフラ (ExpandHelp)
% \item IME-like command etnry interface
% やりたいことを実行するインタフェース (IME的なもの)
\item Help data sharing infrastructure for the above strategy.
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

@@

% \subsection{Entering a command}

We assume that the user uses \tt{bash} for his software
development activities.
% 
When a user wants to compare the latest \stt{README.md} file
with the same file from 2 versions before,
he might try to use {\GIT} with an option
``{\smallfont\verb|HEAD^^|}''
for specifying the old version.

\begin{figure}[h]
  {\smallfont
  \verb|$ git diff HEAD^^ README.md|
  \par
  \verb|$|
  }
  \caption{Invoking \stt{git diff}.}
  \label{gitdiff}
\end{figure}

% \begin{quotation}
%   {\smallfont
%   \verb|$ git diff HEAD^^ README.md|
%   \par
%   \verb|$|
%   }
% \end{quotation}

However, nothing happens here because
\verb|HEAD^^|
specifies a file included in the older commit,
and the command in figure \ref{gitdiff} only compares the
\stt{README.md} with the file included in an old commit, where
\stt{README.md} has not been changed since then.

If {\GH} is installed,
the user can type a special shortcut key
% (e.g. \tt{Cmd-Ctrl-G})
to invoke {\GH} after typing \sqtt{git RE 2} to see how he can
perform the task.

\begin{figure}[h]
  % \includegraphics[width=9cm,bb=0 0 1194 822]{figures/example1.png}
  \includegraphics[width=9cm,bb=0 0 900 600]{figures/example1.png}
  %\includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH} after typing \stt{git read 2}.}
  \label{example1}
\end{figure}

Here, various candidate entries with
descriptions and command strings are listed,
just like text input support systems for non-English languages.
One of the entries says
``\ssf{Compare} \stt{README.md} \ssf{with the one from 2 versions before}'',
and if the user thinks that's what he wants to do,
he can select the entry by typing arrow keys and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like \sqsf{2 days ago} is also shown in the candidate list
of Figure \ref{example1}.
This means that the user can use the same string \sqtt{git RE 2}
for getting the information of \stt{README.md} file of the day before yesterday.
The generated argument
``{\smallfont\verb|@{2 days ago}|}'',
may not be familiar to most {\GIT} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}
without knowing the correct syntax of this option.

When the user types a special shortcut key
after typing \sqtt{git sh reed 3},
entries related to \stt{README.md} file are listed because
\sqtt{reed} is close to \sqtt{README.md}.

\begin{figure}[h]
  %\includegraphics[width=9cm,bb=0 0 1100 760]{figures/example2.png}
  \includegraphics[width=9cm,bb=-100 0 800 550]{figures/example2.png}
  \caption{Invoking {\GH} after typing \stt{git sh reed 3}.}
  \label{example2}
\end{figure}

A Japanese {\GIT} user can do the same thing just like
English-speaking users (Figure \ref{example3}).
He can user the term \qtt{比}, etc. to find how he can perform the job.

\begin{figure}[t]
  % bb=0 0 1290 866
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH} in Japanese environment.}
  \label{example3}
\end{figure}

If the user wants to know more about the command line,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
button and see the Wiki page shown in Figure \ref{scrapboxpage}.
The user can edit the page if he wants to add information or finds an error.
In this page, description part is preceded by a ``\texttt{\$}'' symbol and
the command part is preceded by ``\texttt{\%}''.

\begin{figure}[t]
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
  \centerline{\includegraphics[width=100mm,bb=-50 -50 1100 950]{figures/scrapbox2.png}}
  \caption{A {\SB} page for \tt{git diff}.}
  \label{scrapboxpage}
\end{figure}

@@

A flexible help data retrieval mechanism ``{\EH}'' is used in {\GH}.
%
Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents description of the help entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

\begin{quote}
  \textbf{description}: \\
  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
  \textbf{command}: \\
  {\smallfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^|} \\
  {\smallfont\verb| -- #{$1}|}
\end{quote}

Special symbol like \stt{\#\{files\}} in the description part is expanded to
the list of filenames like \stt{README.md|index.html}.
The first regular expression, the description part,
is for generating texts like
\sqsf{Compare README.md with the one from 1 versions before}, 
\sqsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a {\GIT} command.
In the first example, \sqsf{README.md} and \sqsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
``{\smallfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.

@@

@@

Finding appropriate entries from the (possibly huge) help document space is
performed in two steps.
First, a state transition diagram is generated from the regular expressions
used in the descriptions.
Second, all the description strings are generated by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions from a short specification.
For example, we use a short regular expression
\sqtt{(remove|delete|erase) (data|file)}
for representing expressions like
\sqsf{remove data},\sqsf{erase file}, etc.

Converting a regular expression to a state transition machine is a
straightforward task.
When we have a regular expression
\sqtt{Compare (README.md|index.html|package.json) with the one (1|2|...|10) versions before}, 
we can convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 571 126]{figures/statemachine.pdf}
\caption{State transition diagram for a \stt{git} command description.}
\label{statemachine1}
\end{figure}

@@

\begin{quote}
\small
\ssf{Compare README.md with the one 1 versions before} \\
\ssf{Compare index.html with the one 1 versions before} \\
...\\
\ssf{Compare package.json with the one 10 versions before}\\
\end{quote}

@@

``Generate-and-test''\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}
is a simple and effective strategy used for solving puzzles.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme1.pdf}}
  \caption{A state machine for \qsf{README}.}
  \label{readme1}
\end{figure}

Initially, only the leftmost node is active, but when the
state machine receives \sqsf{R}, both the first and the second node become active,
and the activation state will change to the following pattern.

\begin{figure}[h]
  \centerline{\includegraphics[width=50mm,bb=0 0 439 73]{figures/readme2.pdf}}
  \caption{After receiving \qsf{R}.}
  \label{readme2}
\end{figure}

When \sqsf{README} is given to the state machine,
the rightmost node becomes active.
%
%\begin{figure}[h]
%\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
%\caption{After receiving \qsf{README}.}
%\label{readme3}
%\end{figure}

Although this state machine is a nondeterministic finite state automata (NFA),
only 7 bits are required to represent the active/inactive states of the nodes,
meaning that the whole states can be represented by a single integer value.
Also,
the state transition can be calculated by a simple combination of
logic and bit shift operations.

\subsubsection{Approximate pattern matching using shifter algorithm}

The state machine shown in Figure \ref{readme1} can accept only one pattern
(\sqsf{README}), but
it can be easily expanded to detect texts that contain a word
similar to the pattern (e.g. \sqsf{REEDEE}).

%   *  ** 
%  risto rante
%  restaurant
% \begin{figure}[htb]
%   \centerline{\includegraphics[width=30mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
%   \caption{Matching error between \qsf{README} and \qsf{REEDEE}.}
%   \label{readme-reddy-mismatch}
% \end{figure}

Adding three more rows of states to Figure \ref{readme1}, we can perform more
flexible pattern matcher which can accept strings with
0 to 3 matching errors.

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-ambig.pdf}}
  \caption{A pattern matcher accepting 0-3 errors.}
  \label{shifterambig}
\end{figure}

Figure \ref{shifterambig} shows a state machine that can detect a string
that matches \sqsf{README} with 0 to 3 mismatches.
Each additional row of nodes represents a matcher with one error,
two errors, and three errors, respectively.
Vertical and diagonal transition edges are added to allow
transitions based on spelling errors.

@@

\begin{figure}[htb]
  \centerline{\includegraphics[width=60mm,bb=0 0 443 282]{figures/readme-reedee.pdf}}
  \caption{Accepting \sqsf{REEDEE}'' using a matcher for \sqsf{README}.}
  \label{readme-reedee}
\end{figure}

The transition of active nodes while reading
\sqsf{REEDEE} is shown in Figure \ref{readme-reedee}.
After reading \sqsf{REEDEE},
only the upper-right node becomes active,
denoting that \sqsf{REEDEE} matches
\sqsf{README}'' with 2 matching errors.

The state transition shown in 
Figure \ref{readme-reedee} looks complicated, but
the matching state can be represented by only four integer variables, and
the matching algorithm can be implemented efficiently.

@@

\paragraph{Applications of {\EH}}
